---
title: "Recommender system"
---

```{r setup, include=FALSE}
library(tm)
library(tidyr)
library(RColorBrewer)
library(wordcloud2)
library(proxy)
library(stringr)
library(slam)
library(topicmodels)
library(MASS)
library(dplyr)
library(cluster)
```



```{r}
setwd("C:/Users/wbc/Desktop/recommender/Airbnb_data")
listing = read.csv(file = "listings1.csv", stringsAsFactor=FALSE)
```


# Combine several columns to create content
```{r}
content = listing[,c("id","description","neighborhood_overview","transit","access","neighbourhood_cleansed","neighbourhood_group_cleansed")]

content = unite_(content,"desc_all",c("description","neighborhood_overview","transit","access","neighbourhood_cleansed","neighbourhood_group_cleansed"), sep = "_")
```



# delete special character,"€"
```{r}
content$description = gsub("[^[:alnum:][:space:]']", "",content$desc_all)
```



# text cleaning, make corpus
# Omit null in corpus, because Korean, 
# Japanese has been translated into "????", 
# After removing punctuation, these description are deleted.
```{r}
corpus = VCorpus(VectorSource(content$desc_all))
for( i in 1:6){
  print(corpus[[i]][1])
} 
corpus = tm_map(corpus, content_transformer(tolower))
corpus = tm_map(corpus, removePunctuation)
corpus = tm_map(corpus, stripWhitespace)
corpus = tm_map(corpus, removeNumbers)
corpus = tm_map(corpus, removeWords, stopwords('english'))
corpus = tm_map(corpus, stemDocument)
```



# delete useless words, create dtm 
```{r}
my_stopwords = c(stopwords("english"),"walk","room","stop","singapor","singapore","apartment","within","apart",
                 "will","place","min","minut","road","etc","hrs","check","can","time","area",
                 "stay","locat","take","one","bed","hour","use","local","need","access","line",
                 "high","live","guest","just","station","also","hous","provide","region","provid","mins","minutes",
                 "fulli","servic","away","tabl","quay","veri","centr","via")
dtm = DocumentTermMatrix(corpus,control = list (stopwords = my_stopwords))
dtm_ti = weightTfIdf(dtm)
mat_ti = as.matrix(dtm_ti)
```


#draw wordcloud
```{r}
tf = sort(colSums(as.matrix(dtm)), decreasing=TRUE)
tf = as.data.frame(tf)
tf$V2 = rownames(tf)
tf = tf[,c("V2","tf")]
wordcloud2(tf)
```




# Algorithm 1
##distance between different room descriptions, recommend the top 3 shortest distances 
```{r}
#calculate similarity between items
sim_mat_cos = crossprod_simple_triplet_matrix(t(dtm_ti))/(sqrt(col_sums(t(dtm_ti)^2) %*% t(col_sums(t(dtm_ti)^2))))

# create new dataframe
matrix = matrix(nrow=7907,ncol=6)
simi_recomd = data.frame(matrix)
names(simi_recomd) = c("id","item1","item2","item3","item4","item5")

# impute similarity hotel into dataframe, simi_recomd table is the final result we want
simi_recomd$id = content$id

for(i in c(1:7907)){
simi_recomd[i,2:6] = content[order(sim_mat_cos[i, ], decreasing = T)[2:6],]$id
}
write.csv(simi_recomd, file="F:/simi.csv") 

```





# Algorithm 2
## SVD + clustering
```{r}
#svd -- dimension reduction, to create new features(but meaningless)
dtm_svd = svd(dtm_ti)
ds = diag(dtm_svd$d[1:3])                    # diag matrix shows the importance of the feature
plot(1:length(dtm_svd$d), dtm_svd$d)       
v = dtm_svd$v
vs = t(as.matrix(v[1:3,]))
v_dtm_N = data.frame(t(as.matrix(v[1:300,]))) # take top300 as the feature, show new td-idf
```


# split 200 rooms' descriptions to do svd
```{r}
dtm_ti = dtm_ti[c(1:1000),]
dtm_svd = svd(dtm_ti)
ds = diag(dtm_svd$d[1:3])                    # diag matrix shows the importance of the feature
plot(1:length(dtm_svd$d), dtm_svd$d) 
v = dtm_svd$v
vs = t(as.matrix(v[1:3,]))
v_dtm_N = data.frame(t(as.matrix(v[1:20,])))
```

# choose appropriate k to find the smallest sum of error square 
```{r}
wssplot = function(data, nc=15, seed=1234){
    wss = vector() 
    #wss = (nrow(data)-1)*sum(apply(data,2,var))
    for (i in 2:nc){
        set.seed(seed)
        wss[i] = sum(kmeans(data, centers=i)$withinss)
        }
    plot(1:nc, wss, type="b", xlab="Number of Clusters",
        ylab="Within groups sum of squares")}
wssplot(v_dtm_N)
# visualization
library(factoextra)
km.res <- kmeans(v_dtm_N,5)
fviz_cluster(km.res, data = v_dtm_N)

```


```{r}
#clustering for recommendation
km = kmeans(v_dtm_N,8) # 10 clusters 
km$cluster
clusters = as.factor(km$cluster)
km$size
table(clusters10)
y_label=content$id
cluster_table = data.frame(id = y_label, class = km.10$cluster) # create table, each id has a cluster
write.csv(cluster_table, file="F:/cluster_recomd.csv")
```





# Algorithm 3
##LDA + TopicModelling

```{r}
# use the perplexity to find the appropriate topic number
perplexity_df = vector()
topics <- c(2:15)
burnin = 100
iter = 1000
keep = 50  

set.seed(1234)
for (i in topics){
 
  fitted = LDA(dtm, k = i, method = "Gibbs",
                control = list(burnin = burnin, iter = iter, keep = keep) )
  perplexity_df[i] <- perplexity(fitted, newdata = dtm)
}
perplexity_df = data.frame(perplexity_df)
perplexity_df$num = c(1:15)
 
# plot
library(ggplot2)
ggplot(perplexity_df, aes(x = num, y = perplexity_df))+geom_line()+geom_point()+
  labs(x = "Number of topics", y = "Perplexity index", title = "Using perplexity index to find the optimal number of topics")+theme_classic()

```


```{r}
lda_8_g = LDA(dtm, 8, method="Gibbs") # use LDA to construct 8 topics

terms(lda_8_g, 10)   # check the most 8 frequent words occuring words in 8 topics

tabulate(topics(lda_8_g))  # check the number of documents in every topic

t(topics(lda_8_g, 3))[1:20,]  # check the most likely 3 topics for the first 20 documents

topic_dataframe = data.frame(t(topics(lda_8_g, 3))[1:7907,])  # create dataframe for topic result
names(topic_dataframe) = c("topic1","topic2","topic3","id","prob")
topic_dataframe$id = content$id
for (i in c(1:7907)) {
  topic_dataframe[i,5] = max(lda_8_g@gamma[i,])
}

write.csv(topic_dataframe, file = "C:/Users/wbc/Desktop/recommender/topic_dataframe.csv")
```

